\center \fontsize{18.8}{20} \selectfont Towards Globally Color-Dual All-Loop Integrands

### 2023-09-12 notes/2loopNLSM.tex
Update 2loopNLSM.tex

In this work, we will consider three different types of cubic representations, that we define below: 
\be
\stackrel{\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}}{\text{Fundamental}}\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
\ee
In this review, we will present examples of this distinct kinematic representations that have appeared in the literature. Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing. The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \citepls{}. We will briefly review the perturbative construction of this theory below.

@@

As part of attemtping to construct a color-kinematics dual
representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
assumptions in searching for double-copyable integrand numerators (ordered according to the
reference):
\begin{enumerate}
\item \textbf{Locality}: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
\item  \textbf{Power-counting:} The maximum power of the loop momenta in the
  numerator is bounded by Feynman-gauge Feynman rules.
\item  \textbf{Cubic diagrams}: The only diagrams with nonzero numerators are
  those with strictly cubic vertices.  This is generally a requirement
  to properly define the kinematic Jacobi relations.
\item  \textbf{Relabeling}: The diagram numerators are only a function of the
  diagram's topology and labeling.
\item  \textbf{Symmetries}: The diagram numerators are invariant under the
  automorphisms of the diagrams \emph{including signs that compensate
    for color-factor sign changes}.
\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the
  physical unitarity cuts of the theory.
\item  \textbf{Color-kinematics duality}: The numerators obey some form of the
  kinematic Jacobi relations.
\end{enumerate}
Point 1 is generally a matter of convenience: there are many examples
in which ``numerators'' with controlled rational contributions have
been found
\cite{Square,WeinzierlBCJLagrangian,Mogull:2015adi,FivePointN4BCJ,Johansson:2017bfl}.
However, without a guiding principle about what types of rational
terms to use, the size of ans\"{a}tze quickly get out of hand.  Point
2 was motivated at the time by the hope that color-dual numerators
could arise naturally out of a special gauge choice. \jm{I'm not sure
  that we should bring up point 2.  I don't follow it and I don't
  think Alex did either since this wouldn't be the most general
  ansatz.  Also, why doesn't point 5 cover point 4?}\ace{I paraphrased
  these out of \cite{Bern:2015ooa}, thus the inclusion of Point 2.
  For Points 4 and 5, definitely 4 $\not \Rightarrow$ 5.  In the other
  direction, I could imagine a situation in which we violate 4 (eg we
  need to specify a reference ordering) but that symmetries are still
  respected as long as you also perform the correct actions on the
  auxiliary data.} On the other hand, recent work by Ben-Shahar,
Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
  good examples?}  demonstrates that constructing Feynman rules which
produce manifestly color-dual numerators for the NMHV sector of
Yang--Mills requires introducing additional auxiliary fields,
including higher-spin modes, which could shift the expected power
counting in non-trivial ways.  Point 3 is a requirement of the BCJ
double-copy: currently there is no known way of incorporating
non-cubic diagrams into the kinematic Jacobi relations.  Points 4 and
5 will be elaborated on in \cref{sec:syms}, Point 6 in
\cref{sec:unitarity}, and Point 7 in \cref{sec:jac-rels}.

@@

\section{One-loop cubic construction}
Here we'll describe the why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well. It has to do with out the vector state sum mixes with the four-point contact. In terms of our previously defined Feynman rules, the three-point YM vertex takes the form:
\be
\cubic{hgrey0}{gluon}{}{gluon}{}{gluon}{}  =  \cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed} + \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} + \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} +\text{h.c.}
\ee
The state-sum between two three-point gluon vertex yields the following expansion in terms of YZ-theory vertices:
\be
 \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
\ee
All the $(\epsilon\epsilon)^1$ diagram permutations are isolated to the cubic sector and together manifest color-kinematics duality. However, the exception of the last diagram which introduces a $(\epsilon\epsilon)^2$ factor, must conspire with the Yang-Mills contact to preserve the duality off-shell

@@

@@

\appendix
\section{Catalog of color-dual theories}
\label{sec:CKLagrangians}
In the next section we will construct one-loop color-dual numerators using Lagrangian descriptions that are manifestly color-dual. As we will show, taking forward limits of tree-level numerators works as long as one can construct an off-shell description with a Lagrangian. Here we briefly review the off-shell examples of the kinematic algebra that will be relevant in this paper. 
\mathcal{L}^{\text{semi-YM}} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} = - \frac{1}{2} G_{\mu\nu} F^{\mu\nu} - \frac{g}{2} G_{\mu\nu} [A_\mu, A_\nu]
\jm{I believe this Lagrangian has a name -- BF theory.  All this does is set F=0 and if you impose Lorenz gauge then you get many of the known color-dual theories.}
\paragraph{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
\be\label{SDcon}
F_{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength. Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
D^\mu F^{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills. In this paper, we will focus on the perturbative aspects of this constraint. Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
u = t+x,\quad v=t-x, \quad w = y+iz
which gives the following expression for the invariant line element:
ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
\begin{align} \label{SDLightCone1}
F_{uw} &=0\,,
 \label{SDLightCone2}
 F_{uv} &= F_{w\bar{w}}\,,
 \label{SDLightCone3}
 F_{v\bar{w}} &= 0\,,
Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
\be\label{SDDef}
A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
Using this definition on the final \jm{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
\be\label{SDEOM}
(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}. In this form, we can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex. Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.

@@

Dimensions will generically be away from four, in $D=4-2\epsilon$, with $\epsilon$ arbitrary. As noted, it will be convenient to take $D\rightarrow 4$ in certain circumstances after integration.  In such cases we will employ appropriate spinor-helicity variables.  Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. For massless momenta, $k_a$ and $k_b$, we have 

@@

Before proceeding, we note a strange property of the $n$-gon numerator for the pions. In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs). However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble. The BEL diagram can be reconstructed from the $n$-gon as follows:
N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$. Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram. 
\section{Notes to self -- James}
\item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
\item Cite papers arguing about whether NLSM in 2D is non-trivial or not.
\item Explain why you need to take a certain portion of the YZ numerator to get the right answer.  Basically you can't have a vector particle circle the loop -- NLSM is a scalar theory so only scalar DOF should actually live in cuts.  If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
\item Reiterate that the (tree) amplitudes of CS and SDYM are zero.
\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
This observation is due to other people but an easy way to see it.
ZM and 2D NLSM have the same EOM after a field redefinition.
This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
\item Forcing pions to match ZM in 2D does funny things.
The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
For 4pt tree, $z=2/3$ (I matched the half ladder).
For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
For 6pt tree, $z$ is 12/35 (I matched the half ladder).
So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
\item Explain how matching to ZM is a little silly.
Check that NLSM and ZM numerator agree on cuts.
Can't do that or else it becomes subtle.
Only well defined object is numerator.
\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.  So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\epsilon$ identities.  Make an ansatz where you do every pairing of $\epsilon$'s.  This doesn't work.
\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
\item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4pt, 6pt, and 8pt.
\item Should probably give the 4pt pion amplitude somewhere to show my conventions.

>>>>

In this work, we will consider three different types of cubic representations, that we define below: 
\be
\qquad\qquad \stackrel{\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{}}{\text{Bifundamental}}\qquad\qquad \stackrel{\Acubic{hgrey0}{}{nhpBlue}{}{nhpBlue}{}{nhpBlue}}{\text{Adjoint}}
\ee
In this review, we will present examples of this distinct kinematic representations that have appeared in the literature. Though from the get go, we stress that in this work we are interested in identifying the analog of adjoint representations of the kinematic numerators; those for which all legs are equally preferrenced by the functional dressing. The only non-trivial $S$-matrix in the literature that exhibits this property to all-loop order, is that of Zakharov-Mikhailov theory \citepls{}. We will briefly review the perturbative construction of this theory below.

@@

As part of attemtping to construct a color-kinematics dual
representation for $\mathcal{N}=0$ Yang--Mills at two loops, Bern,
Davies, and Nohle (BDN) \cite{Bern:2015ooa} lay out the following core
assumptions in searching for double-copyable integrand numerators (ordered according to the
reference):
\begin{enumerate}
\item \textbf{Locality}: Diagram ``numerators'' are polynomials in momenta and
  polarizations, \eg the diagrams only have poles given by the
  propagators of the diagrams.
\item  \textbf{Power-counting:} The maximum power of the loop momenta in the
  numerator is bounded by Feynman-gauge Feynman rules.
\item  \textbf{Cubic diagrams}: The only diagrams with nonzero numerators are
  those with strictly cubic vertices.  This is generally a requirement
  to properly define the kinematic Jacobi relations.
\item  \textbf{Symmetries}: The diagram numerators are only a function of the
  diagram's topology and labeling. The diagram numerators are invariant under the
  automorphisms of the diagrams \emph{including signs that compensate
    for color-factor sign changes}.
\item  \textbf{Unitarity cuts}: The cuts of the ansatz must reproduce the
  physical unitarity cuts of the theory.
\item  \textbf{Color-kinematics duality}: The numerators obey some form of the
  kinematic Jacobi relations.
\end{enumerate}
Point 1 is generally a matter of convenience: there are many examples
in which ``numerators'' with controlled rational contributions have
been found
\cite{Square,WeinzierlBCJLagrangian,Mogull:2015adi,FivePointN4BCJ,Johansson:2017bfl}.
However, without a guiding principle about what types of rational
terms to use, the size of ans\"{a}tze quickly get out of hand.  Point
2 was motivated at the time by the hope that color-dual numerators
could arise naturally out of a special gauge choice. \jm{I'm not sure
  that we should bring up point 2.  I don't follow it and I don't
  think Alex did either since this wouldn't be the most general
  ansatz.  Also, why doesn't point 5 cover point 4?}\ace{I paraphrased
  these out of \cite{Bern:2015ooa}, thus the inclusion of Point 2.
  For Points 4 and 5, definitely 4 $\not \Rightarrow$ 5.  In the other
  direction, I could imagine a situation in which we violate 4 (eg we
  need to specify a reference ordering) but that symmetries are still
  respected as long as you also perform the correct actions on the
  auxiliary data.} On the other hand, recent work by Ben-Shahar,
Garozzo, and Johansson \cite{Ben-Shahar:2022ixa} \ace{Are there other
  good examples?}  demonstrates that constructing Feynman rules which
produce manifestly color-dual numerators for the NMHV sector of
Yang--Mills requires introducing additional auxiliary fields,
including higher-spin modes, which could shift the expected power
counting in non-trivial ways.  Point 3 is a requirement of the BCJ
double-copy: currently there is no known way of incorporating
non-cubic diagrams into the kinematic Jacobi relations.  Points 4 and
5 will be elaborated on in \cref{sec:syms}, Point 6 in
\cref{sec:unitarity}, and Point 7 in \cref{sec:jac-rels}.

@@

\section{One-loop cubic construction}
Here we'll describe the why constructing the full Yang-Mills kinematic algebra (outside self-dual sector) is generically hard, and why the same reason makes NLSM beyond one-loop hard as well. It has to do with how the vector state sum mixes with the four-point contact.

This is most easily seen by decomposing the Yang-Mill three-point interaction in terms of the following vertex in Lorenz gauge:
\be \label{YMSvert}
\Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} = (\varepsilon_1\varepsilon_2)(\varepsilon_3 k_1)
\ee
With this, the full vector interaction can be expressed as a sum over cyclic permutations:
\be
\cubic{hgrey0}{gluon}{}{gluon}{}{gluon}{}  =  \cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed} + \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} + \Acubic{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{} +\text{h.c.}
\ee
The state-sum between two three-point gluon vertex yields the following expansion in terms of YZ-theory vertices:
\be
 \AcubicB{hgrey0}{gluon}{}{gluon}{}{gluon}{}{gluon}{} =  \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{fermion2}{} + 5 \text{ perms} + \AcubicB{hgrey0}{}{nhpRed}{}{nhpRed}{fermion2}{}{}{nhpRed}
\ee
where we have defined a new oriented vertex in terms of our scalar-vector building block of \ref{YMSvert},
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} = \cubic{hgrey0}{}{nhpRed}{fermion2}{}{}{nhpRed} +\cubic{hgrey0}{fermion2}{}{}{nhpRed}{}{nhpRed}\,.
\ee
All the $(\epsilon\epsilon)^1$ diagram permutations are isolated to the cubic sector and together manifest color-kinematics duality. However, the exception of the last diagram which introduces a $(\epsilon\epsilon)^2$ factor, must conspire with the Yang-Mills contact to preserve the duality off-shell

@@

\mathcal{L}^{\text{semi-YM}} = -\frac{1}{2}\text{tr}\left[\bar{F}_{\mu\nu}F^{\mu\nu}\right]
where,
\bar{F}^a_{\mu\nu} = \partial_\mu \bar{A}_\nu^a - \partial_\nu \bar{A}_\mu^a
F^a_{\mu\nu} = \partial_\mu A_\nu^a - \partial_\nu A_\mu^a

@@

\appendix
\section{Catalog of color-dual theories}
\label{sec:CKLagrangians}
\paragraph{Self-Dual Yang-Mills} The first example in the literature \citepls{} of color-dual Feynman rules is that of Yang-Mills theory in the self-dual sector (SDYM):
\be
\mathcal{L}^{\text{YM}} = -\frac{1}{4}F_{\mu\nu}F^{\mu\nu}
\ee
To obtain the Lagrangian for self-dual Yang-Mills, we applyy the self-dual condition that equates the field strength to its dual 2-form:
\be\label{SDcon}
F_{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}F^{\rho\sigma}
\ee
where $F_{\mu\nu} = \partial_\mu A_\nu -\partial_\nu A_\mu + g[A_\mu ,A_\nu]$ is the non-abelian $SU(N)$ field strength. Solutions to the self-dual condition automatically satisfy the Yang-Mills equation of motion due to the Bianchi identity:
\be
D^\mu F^{\mu\nu} = \frac{1}{2} \epsilon_{\mu\nu\rho\sigma}D^\mu F^{\rho\sigma} = 0
\ee
Solutions to \cref{SDcon} correspond to instanton configurations that are probed by the gauge field path integral in the full non-perturbative description of Yang-Mills. In this paper, we will focus on the perturbative aspects of this constraint. Transforming from Cartesian coordinates to light cone coordinantes, $(t,x,y,z) \rightarrow (u,v,w,\bar{w})$, which take the following definition:
\be
u = t+x,\quad v=t-x, \quad w = y+iz
\ee
which gives the following expression for the invariant line element:
\be
ds^2 = 2(dudv - dwd\bar{w}) = dt^2 - d\vec{x}\cdot d\vec{x}
\ee
Applying this coordinate transformation to the self-dual condition of \cref{SDcon}, we obtain the following three constraint equations from the original three cartesian coordinate expressions:
\begin{align} \label{SDLightCone1}
F_{uw} &=0\,,
\\
 \label{SDLightCone2}
 F_{uv} &= F_{w\bar{w}}\,,
\\
 \label{SDLightCone3}
 F_{v\bar{w}} &= 0\,,
\end{align}
Thus, in light-cone gauge, $A_u=0$, we obtain the follow set of equations that are one-to-one with the self-dual condition:
\be
A_u=0 \text{ and } (\ref{SDLightCone1}) \quad\Rightarrow \quad A_w=0
\ee
The \cref{SDLightCone2} then implies the following that $A_v$ and $A_{\bar{w}}$ depend on a single degree of freedom
\be
A_w=0\,,\,A_u=0 \text{ and } (\ref{SDLightCone2}) \quad\Rightarrow \quad \partial_u A_v = \partial_w A_{\bar{w}}
\ee
This constraint is  satisfied with the following definition of the gauge field in terms of a single scalar degree of freedom which we call $\Psi$:
\be\label{SDDef}
A_v = \frac{1}{2} \partial_w \Psi, \qquad A_{\bar{w}} = \frac{1}{2} \partial_u \Psi,
\ee
Using this definition on the final \jm{first?} self-dual constraint equation thus yields the following equation of motion for the dynamical scalar field:
\be\label{SDEOM}
(\ref{SDLightCone1}) \text{ and } (\ref{SDDef}) \quad  \Rightarrow\quad \Box \Psi + ig [\partial_u \Psi, \partial_w \Psi ]=0
\ee
Adding back in the anti-holomorphic field $\bar{\Psi}$ as a Lagrange multiplier, we obtain the following interaction Lagrangian for self-dual Yang-Mills theory:
\begin{eBox}
\be
\mathcal{L}^{\text{SDYM}} = (\partial \bar{\Psi})(\partial \Psi) -i g \bar{\Psi} [\partial_u \Psi, \partial_w \Psi ]
\ee
\end{eBox}
The color-ordered ordered cubic Feynman rule for this theory can be immediately read off as follows:
\be
\cubic{hgrey0}{fermion2}{}{fermion2}{}{fermion2}{} =X(k_1,k_2) \equiv k_{u,1}k_{w,2} - k_{w,1}k_{u,2}
\ee
In this form, the Lagrangian and Feynman rules are manifestly color-dual \textit{off-shell}. In this form, we can see the effect \cref{SDcon} had on the Feynman rules of the full Yang-Mills Lagrangian: it simply decoupled the anti-MHV three-point vertex from the theory, leaving only the MHV three-point vertex. Before proceeding, it is important to note that the mass-dimension of the theory appears to differ from that of Yang-Mills -- we comment on this in detail in our appendix on spinor-helicity variables and conventions.

@@

Here we apply the same conventions of Ref.~\cite{jjmcTASI2014}, which we quote now. For massless momenta, $k_a$ and $k_b$, we have 

@@

Before proceeding, we note a strange property of the $n$-gon numerator for the pions. In this form, Jacobi relations produce \textit{non-vanishing} values for bubbles on external legs (BELs). However, it is easy to see that the contribution integrates to zero after applying IBP relations/tensor reduction on the bubble. The BEL diagram can be reconstructed from the $n$-gon as follows:
\be
N^{\text{BEL}}_{1|2,34} = N^{\text{NLSM}}_{(1234,l)}-N^{\text{NLSM}}_{(1243,l)}-N^{\text{NLSM}}_{(1342,l)}+N^{\text{NLSM}}_{(1432,l)}
\ee
where we define the loop momentum to be in between the left most and right most leg on the box. Plugging in particular values for $l_i$, we obtain the following expression for the BEL
\be
N^{\text{BEL}}_{1|2,34} = s_{12} (l+k_1)^2 l^{\mu} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} 
\ee
Notice there is an overall factor that cancels one of the propagators. Plugging this in, produces an integral of the following form
\be
\mathcal{I}^{\text{BEL}}_{1|2,34} = s_{12} k_1^{\nu} k_2^{[\mu} k_{[34]}^{\nu]} \int \frac{d^D l}{i\pi^{D/2}} \frac{l^\mu }{l^2-\mu^2} \sim   s_{12}(s_{13}-s_{14}) (\mu^2)^{D/2}
\ee
where we have introduced a mass regulator that will be proportional the the on-shell momentum inside the BEL, $\mu^2 \equiv k_1^2$. Thus, in large enough dimension, this integral suppresses the $\mu^{-2}$ divergence appearing in the denominator of the BEL diagram.

\section{Notes to self -- James}
\jm{Notes to self -- James}
\begin{itemize}
\item We should comment on 1-loop YM.  Can you easily write down the $n$-gon numerator?  I have some memory that someone has some complicated YM numerator.
\item Cite papers arguing about whether NLSM in 2D is non-trivial or not.
\item Explain why you need to take a certain portion of the YZ numerator to get the right answer.  Basically you can't have a vector particle circle the loop -- NLSM is a scalar theory so only scalar DOF should actually live in cuts.  If you have a tree then you plug in longitudinal modes but if you have a loop then you really need to remove vector modes so that only scalars circle the loop.
\item Reiterate that the (tree) amplitudes of CS and SDYM are zero.
\item ZM and 2D NLSM (PCM) are the same classically but not quantum mechanically.
This observation is due to other people but an easy way to see it.
ZM and 2D NLSM have the same EOM after a field redefinition.
This means that the classical physics is the same but of course the Lagrangians aren't the same and the field redefinition can change the path integral measure.
\item Forcing pions to match ZM in 2D does funny things.
The pion coupling constant is dropped but is implicitly set by the ordered 4pt amplitude which is normalized to be $-k_1 \cdot k_3$ in the package.
I've tabulated what happens when you take a general D NLSM answer and force it to match ZM in 2D.
Let's say that $n_\text{NLSM} = z n_\text{ZM}$ in 2D where I'm matching basis/master numerators.
For 4pt tree, $z=2/3$ (I matched the half ladder).
For 4pt 1-loop, $z$ is free/pure generalized gauge (I matched the box).
For 4pt 2-loop (when you impose certain $\ell$ power counting) $z$ is $216/565=\tfrac{2^3 3^3}{5 \cdot 113}$ (I matched the double box and penta-triangle).
For 6pt tree, $z$ is 12/35 (I matched the half ladder).
So you can match kinematic structure (the combination of Mandelstams) of NLSM to ZM in 2D but you can't get the coupling constant right at loop level, that is, ZM is a different theory quantum mechanically.
Actually these numbers make it look like you can't even match the theories classically but I guess for the theories to match classically you only need the amplitudes to agree and I matched numerators.
\item Explain how matching to ZM is a little silly.
Check that NLSM and ZM numerator agree on cuts.
Can't do that or else it becomes subtle.
Only well defined object is numerator.
\item At 4pt 1-loop $\prod p_L^2 -p_R^2$ agrees with the ZM answer $\prod p_L \eps p_R$ up to some number.
At 6pt 1-loop this is not true and the two answers differ by alternating signs depending on the kinematic configuration.
\item You cannot lift ZM to general D NLSM in the democratic way that Nic described because it fails at 6pt tree.  So you take the ZM answer that looks like $\langle 1 2\rangle \langle 3 4\rangle...$ you can convert every pair of angles to dot products using 2D $\epsilon$ identities.  Make an ansatz where you do every pairing of $\epsilon$'s.  This doesn't work.
\item To clean up the NLSM 4pt 2-loop answer I forced the answer to match ZM in 2D.
The ZM answer also only has certain powers of loop momenta $\ell^5$...$\ell^8$ where $\ell$ represents any combination of $\ell_1$ and $\ell_2$.
I enforce this $\ell^5$...$\ell^8$ behavior on the NLSM ansatz too.
\item Describe Jacobi:  s,t,u channel color factors sum to zero so you want numerators to do the same
\item Remember that I've explicitly checked the nice form of the 1-loop NLSM numerators at 4pt, 6pt, and 8pt.
\item Should probably give the 4pt pion amplitude somewhere to show my conventions.
\end{itemize}
